### 2025-08-26 getting-started.qmd
20250826 - formatting

@@

The [`petersenlab`](https://cran.r-project.org/web/packages/petersenlab/index.html) package [@R-petersenlab] has a convenience function, `petersenlab::\`%ni%\``, for the logical operator of determining whether an element is *not* in a value of another vector:

>>>>

``base::`%in%` ``:

@@

The [`petersenlab`](https://cran.r-project.org/web/packages/petersenlab/index.html) package [@R-petersenlab] has a convenience function, ``petersenlab::`%ni%` ``, for the logical operator of determining whether an element is *not* in a value of another vector:
